### 2018-09-03 Sections/QTCP_protocol_stack.tex

\begin{figure}[!htbp]\index{QTCP protocol stack}
\includegraphics[width=0.475\textwidth]{stack}
\captionspace \caption{Protocol stack for QTCP. The protocol stack mediates communication of quantum data from Alice to Bob using the shown layers of abstraction. The end goal is to provide Bob a virtual interface to Alice's transmitted data, while remaining oblivious to the underlying protocol.} \label{fig:stack}\index{QTCP protocol stack}
\end{figure}

@@

\startalgtable
\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Transport(Packet):
\begin{enumerate}
    \item nextNode = Packet.RoutingQueue.Pop()
    \item Packet.PhysicallySendTo(nextNode)
    \item Packet.WaitUntilArrivesAt(nextNode)
    \item checksum = Hash(Packet.Header + Packet.ClassicalData)
    \item if(checksum $\neq$ Packet.Header.Checksum) \{
    \setlength{\itemindent}{0.2in}
    \item Packet.Sender.Notify(\textsc{Failure})
    \item Packet.Recipient.Notify(\textsc{Failure})
    \item Packet.Discard()
    \item $\Box$
        \setlength{\itemindent}{0in}
\item \}
    \item Packet.Costs += IncomingLink.Costs
    \item Packet.Attributes.Update()
    \item if(Packet.RoutingQueue.Length = 0) \{
    \setlength{\itemindent}{0.2in}
    \item Return(Packet)
        \setlength{\itemindent}{0in}
    \item \}
    \setlength{\itemindent}{0in}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{Algorithm implemented by the \textsc{Transport} layer of QTCP for each \textsc{Packet}. The \texttt{Attributes.Update()} function is left undefined. This is where arbitrary \textsc{Attribute} dynamics may take place.} \label{alg:transport_alg}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Reconstruction(Packets):
\begin{enumerate}
    \item Packets.WaitUntilAllReceived()
    \item message =\\ 
    Packets.SortByOrderAscending().data
    \item Packets.Receiver.Notify(message)
     \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{The goal of the \textsc{Reconstruction} layer, is to take a collection of received \textsc{Packets} and reassemble them into the \textsc{Message}.} \label{alg:reconstruction}
\end{table}

>>>>

\begin{figure}[!htbp]\index{QTCP protocol stack}
\includegraphics[width=0.475\textwidth]{stack}
\captionspacefig \caption{Protocol stack for QTCP. The protocol stack mediates communication of quantum data from Alice to Bob using the shown layers of abstraction. The end goal is to provide Bob a virtual interface to Alice's transmitted data, while remaining oblivious to the underlying protocol.} \label{fig:stack}\index{QTCP protocol stack}
\end{figure}

@@

\startalgtable
\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Transport(Packet):
\begin{enumerate}
    \item nextNode = Packet.RoutingQueue.Pop()
    \item Packet.PhysicallySendTo(nextNode)
    \item Packet.WaitUntilArrivesAt(nextNode)
    \item checksum = Hash(Packet.Header + Packet.ClassicalData)
    \item if(checksum $\neq$ Packet.Header.Checksum) \{
    \setlength{\itemindent}{0.2in}
    \item Packet.Sender.Notify(\textsc{Failure})
    \item Packet.Recipient.Notify(\textsc{Failure})
    \item Packet.Discard()
    \item $\Box$
        \setlength{\itemindent}{0in}
\item \}
    \item Packet.Costs += IncomingLink.Costs
    \item Packet.Attributes.Update()
    \item if(Packet.RoutingQueue.Length = 0) \{
    \setlength{\itemindent}{0.2in}
    \item Return(Packet)
        \setlength{\itemindent}{0in}
    \item \}
    \setlength{\itemindent}{0in}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Algorithm implemented by the \textsc{Transport} layer of QTCP for each \textsc{Packet}. The \texttt{Attributes.Update()} function is left undefined. This is where arbitrary \textsc{Attribute} dynamics may take place.} \label{alg:transport_alg}
\end{table}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Reconstruction(Packets):
\begin{enumerate}
    \item Packets.WaitUntilAllReceived()
    \item message =\\ 
    Packets.SortByOrderAscending().data
    \item Packets.Receiver.Notify(message)
     \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{The goal of the \textsc{Reconstruction} layer, is to take a collection of received \textsc{Packets} and reassemble them into the \textsc{Message}.} \label{alg:reconstruction}
\end{table}

### 2018-09-03 Sections/economics_of_the_quantum_internet.tex

\captionspacealg \caption{Summary of the dynamics of various economic models under several computational scaling functions ($f_\mathrm{sc}$) of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\mathrm{global}=\sum_{j\in \mathrm{nodes}} n_j$} qubits in the global network. $N_0$ is the initial number of qubits, undergoing growth rate $\gamma_N$. $C_0$ is the initial monetary cost per qubit, undergoing decay rate $\gamma_C$. $\gamma_\mathrm{ror}$ is the rate of return on the licensing of compute-time on qubits, and $r_\mathrm{rf}$ is the risk-free rate of return. $\gamma_T$ is the rate of taxation, and $N_\mathrm{tax}$ is the number of qubits that would exist on the network in the absence of taxation.} \label{tab:summary_ec_models}

>>>>

\captionspacetab \caption{Summary of the dynamics of various economic models under several computational scaling functions ($f_\mathrm{sc}$) of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\mathrm{global}=\sum_{j\in \mathrm{nodes}} n_j$} qubits in the global network. $N_0$ is the initial number of qubits, undergoing growth rate $\gamma_N$. $C_0$ is the initial monetary cost per qubit, undergoing decay rate $\gamma_C$. $\gamma_\mathrm{ror}$ is the rate of return on the licensing of compute-time on qubits, and $r_\mathrm{rf}$ is the risk-free rate of return. $\gamma_T$ is the rate of taxation, and $N_\mathrm{tax}$ is the number of qubits that would exist on the network in the absence of taxation.} \label{tab:summary_ec_models}

### 2018-09-03 Sections/encrypted_cloud_quantum_computing.tex

\begin{figure}[!htbp]
\includegraphics[width=0.425\textwidth]{gen_pass_hom}
\captionspace \caption{General structure for the relationship between the encoding ($\hat{E}$), decoding ($\hat{D}$), and computational ($\hat{U}$) operations in a passive, non-interactive, optical quantum computation, where Alice is restricted to non-entangling, single-mode encoding and decoding operations.} \label{fig:gen_pass_hom}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function PolarisationKeyEncoding($S$,$k$):
\begin{enumerate}
    \item Alice meditates upon, but needn't actually prepare the state,
    \begin{align}
    \ket\psi_\mathrm{number} = \ket{S_1,\dots,S_m},    
    \end{align}
    where,
    \begin{align}
S_i\in\{0,1\},
    \end{align}
is the photon-number of the $i$th mode.
   \item Alice makes the substitutions from the photon-number basis into the polarisation basis, 
   \begin{align}
   \ket{0}&\to\ket{H}, \nonumber \\
   \ket{1}&\to\ket{V},
   \end{align}
   to obtain $\ket\psi_\mathrm{pol}$, containing $m$ photons in total, one per mode.
   \item Alice chooses a random private key $k$ as a real number from the uniform distribution,
   \begin{align}
    k\in(0,2\pi).
    \end{align}
    \item Alice prepares the encoded state by applying the same polarisation rotation (using wave-plates), of angle $k$, to each mode,
   \begin{align}
   \ket\psi_\mathrm{enc} = \hat{R}(k)^{\otimes m}\ket\psi_\mathrm{pol},
   \end{align}
   where,
   \begin{align}
   \hat{R}(\theta) = \left(\begin{array}{cc}
\cos\theta & -\sin\theta \\
\sin\theta & \cos\theta \end{array}\right).
   \end{align}
    \item Alice sends $\ket\psi_\mathrm{enc}$ to Bob.
    \item Bob applies processing using his linear optics computer, to obtain,
    \begin{align}
    \ket\psi_\mathrm{enc\,comp} = \hat{U} \ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns $\ket\psi_\mathrm{enc\,comp}$ to Alice.
    \item Alice applies the inverse of the encoding operation,
    \begin{align}
    \ket\psi_\mathrm{comp} = \hat{R}(-k)^{\otimes m}\ket\psi_\mathrm{enc\,comp}.
    \end{align}
    \item Alice applies polarisation filters to $\ket\psi_\mathrm{comp}$, discarding horizontally polarised photons.
    \item The remaining vertically polarised state is Alice's unencrypted output of the computation.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics, using polarisation-key encoding.} \label{alg:homo_LO}
\end{table}

\begin{figure}[!htbp]
\includegraphics[width=0.425\textwidth]{BS_homo}
\captionspace \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics. Horizontal bars are wave-plates, implementing polarisation rotations $\hat{R}(\theta)$ -- the encryption and decryption operations performed by Alice. $\ket\psi_\mathrm{in}$ contains one photon per mode, polarisation-encoded such that vertically polarised photons belong to the desired computation, whilst the remaining horizontally polarised ones are dummies. The polarisation rotation angle, $k$, acts as Alice's private key. The photo-detectors are polarisation-resolving, discarding all dummy horizontally polarised photons at the output. The algorithm is described in detail in Alg.~\ref{alg:homo_LO}.} \label{fig:BS_homo}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function PhaseKeyEncoding($\vec\alpha$,$k$):
\begin{enumerate}
    \item Alice prepares the input multi-mode coherent state,
    \begin{align}
    \ket\psi_\mathrm{in} = \ket{\vec\alpha} = \ket{\alpha_1,\dots,\alpha_m}.
    \end{align}
    \item Alice chooses a random private key $k$ as a real number from the uniform distribution,
    \begin{align}
    k\in (0,2\pi).
    \end{align}
    \item Alice prepares the encoded state by applying the same phase-shift, of angle $k$, to each mode,
    \begin{align}
    \ket\psi_\mathrm{enc} = \hat\Phi(k)^{\otimes m}\ket\psi_\mathrm{in},
    \end{align}
    where,
    \begin{align}
    \hat\Phi(\phi) = e^{i\phi\hat{n}},
    \end{align}
    is the phase-shift operator.
    \item Alice sends $\ket\psi_\mathrm{enc}$ to Bob.
    \item Bob applies processing using his linear optics computer, to obtain,
    \begin{align}
    \ket\psi_\mathrm{enc\,comp} = \hat{U}\ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns $\ket\psi_\mathrm{enc\,comp}$ to Alice.
    \item Alice applies the inverse of the encoding operation,
    \begin{align}
    \ket\psi_\mathrm{comp} = \hat\Phi(-k)^{\otimes m}\ket\psi_\mathrm{enc\,comp}.
    \end{align}
    \item The resulting state is,
    \begin{align}
    \ket\psi_\mathrm{comp} = \ket{\vec\beta} = \ket{\beta_1,\dots,\beta_m},
    \end{align}
    where,
    \begin{align}
    \vec\beta = U\cdot\vec\alpha.
    \end{align}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{Protocol for implementing homomorphic encryption on coherent state passive linear optics, using phase-key encoding.} \label{alg:homo_coherent_LO}
\end{table}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{coherent_state_homo_unenc}\\
\includegraphics[width=0.475\textwidth]{coherent_state_homo_enc}
\captionspace \caption{Trace distance between unencoded (top) and encoded (bottom) basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. Each mode is inputted with one of two basis coherent states, \mbox{$\ket{\pm\alpha}$}. \mbox{$\mathrm{wt}(\vec{x})$} denotes the Hamming weight of bit-string $\vec{x}$. Two states are indistinguishable if their trace distance is 0, and distinguishable (orthogonal) if their trace distance is 1. Lower trace distance between encoded states implies a lower chance of Bob guessing Alice's plaintext input state.} \label{fig:homo_coh_st_tr}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=0.475\textwidth]{coherent_state_homo_unenc}
\includegraphics[width=0.475\textwidth]{coherent_state_homo_enc}
\captionspace \caption{Trace distance between unencoded (top) and encoded (bottom) basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. Each mode is inputted with one of two basis coherent states, \mbox{$\ket{\pm\alpha}$}. \mbox{$\mathrm{wt}(\vec{x})$} denotes the Hamming weight of bit-string $\vec{x}$. Two states are indistinguishable if their trace distance is 0, and distinguishable (orthogonal) if their trace distance is 1. Lower trace distance between encoded states implies a lower chance of Bob guessing Alice's plaintext input state.} \label{fig:homo_coh_st_tr}
\end{figure*}
\fi

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{coherent_state_homo_ratio}
\captionspace \caption{Ratio of the trace distance between unencoded and encoded basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. \mbox{$R<1$} implies information hiding from Bob.} \label{fig:homo_coh_st_ratio}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DisplacementKeyEncoding($\ket\psi$,$k$):
\begin{enumerate}
    \item Alice prepares the $m$-mode state $\ket\psi$.
    \item Alice chooses a set of independent complex displacement amplitudes as her private key,
    \begin{align}
    k=\{\alpha_1,\dots,\alpha_m\}.
    \end{align}
    \item Alice applies the displacements to each mode, yielding her encrypted state,
    \begin{align}
    \ket\psi_\mathrm{enc} = \left[\bigotimes_{i=1}^m \hat{D}_i(\alpha_i)\right] \ket\psi,
    \end{align}
    where $\hat{D}_i(\alpha_i)$ is the displacement operator for the $i$th mode, with displacement amplitude $\alpha_i$.
    \item Alice sends the encrypted state to Bob.
    \item Bob applies the computation $\hat{U}$,
    \begin{align}
    \ket\psi_\mathrm{enc\, comp} = \hat{U}\ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns the encrypted computed state to Alice.
    \item Alice calculates the inverse displacement amplitudes $\vec\beta$,
    \begin{align}
    \vec\beta = U\cdot\vec\alpha.
    \end{align}
    \item Alice applies the inverse displacements to each mode,
    \begin{align}
    \ket\psi_\mathrm{comp} &= \left[\bigotimes_{i=1}^m \hat{D}^\dag_i(\beta_i)\right] \ket\psi_\mathrm{enc\, comp} \nonumber \\
    &= \hat{U}\ket\psi,
    \end{align}
    \item $\ket\psi_\mathrm{comp}$ is the unencrypted computed output state.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{Protocol for implementing homomorphic encryption using displacement-key encoding.} \label{alg:homo_disp_LO}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{lo_displacement_homo}
\captionspace \caption{Circuit layout for displacement-key homomorphic encoding of passive linear optics, where \mbox{$\alpha_i'=\alpha_i/r$} and \mbox{$\beta_i'=\beta_i/r$}. Mixing the input modes with respective coherent states on a very low-reflectivity ($r$) beamsplitter implements the displacement operations. Following decoding, the output states is simply given by \mbox{$\ket{\psi_\mathrm{out}} = \hat{U}\ket{\psi_\mathrm{in}}$}, the computed input state.}\label{fig:lo_disp_key_circuit}	
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[width=0.425\textwidth]{gen_pass_hom}
\captionspacefig \caption{General structure for the relationship between the encoding ($\hat{E}$), decoding ($\hat{D}$), and computational ($\hat{U}$) operations in a passive, non-interactive, optical quantum computation, where Alice is restricted to non-entangling, single-mode encoding and decoding operations.} \label{fig:gen_pass_hom}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function PolarisationKeyEncoding($S$,$k$):
\begin{enumerate}
    \item Alice meditates upon, but needn't actually prepare the state,
    \begin{align}
    \ket\psi_\mathrm{number} = \ket{S_1,\dots,S_m},    
    \end{align}
    where,
    \begin{align}
S_i\in\{0,1\},
    \end{align}
is the photon-number of the $i$th mode.
   \item Alice makes the substitutions from the photon-number basis into the polarisation basis, 
   \begin{align}
   \ket{0}&\to\ket{H}, \nonumber \\
   \ket{1}&\to\ket{V},
   \end{align}
   to obtain $\ket\psi_\mathrm{pol}$, containing $m$ photons in total, one per mode.
   \item Alice chooses a random private key $k$ as a real number from the uniform distribution,
   \begin{align}
    k\in(0,2\pi).
    \end{align}
    \item Alice prepares the encoded state by applying the same polarisation rotation (using wave-plates), of angle $k$, to each mode,
   \begin{align}
   \ket\psi_\mathrm{enc} = \hat{R}(k)^{\otimes m}\ket\psi_\mathrm{pol},
   \end{align}
   where,
   \begin{align}
   \hat{R}(\theta) = \left(\begin{array}{cc}
\cos\theta & -\sin\theta \\
\sin\theta & \cos\theta \end{array}\right).
   \end{align}
    \item Alice sends $\ket\psi_\mathrm{enc}$ to Bob.
    \item Bob applies processing using his linear optics computer, to obtain,
    \begin{align}
    \ket\psi_\mathrm{enc\,comp} = \hat{U} \ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns $\ket\psi_\mathrm{enc\,comp}$ to Alice.
    \item Alice applies the inverse of the encoding operation,
    \begin{align}
    \ket\psi_\mathrm{comp} = \hat{R}(-k)^{\otimes m}\ket\psi_\mathrm{enc\,comp}.
    \end{align}
    \item Alice applies polarisation filters to $\ket\psi_\mathrm{comp}$, discarding horizontally polarised photons.
    \item The remaining vertically polarised state is Alice's unencrypted output of the computation.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics, using polarisation-key encoding.} \label{alg:homo_LO}
\end{table}

\begin{figure}[!htbp]
\includegraphics[width=0.425\textwidth]{BS_homo}
\captionspacefig \caption{Protocol for implementing homomorphic encryption on photonic passive linear optics. Horizontal bars are wave-plates, implementing polarisation rotations $\hat{R}(\theta)$ -- the encryption and decryption operations performed by Alice. $\ket\psi_\mathrm{in}$ contains one photon per mode, polarisation-encoded such that vertically polarised photons belong to the desired computation, whilst the remaining horizontally polarised ones are dummies. The polarisation rotation angle, $k$, acts as Alice's private key. The photo-detectors are polarisation-resolving, discarding all dummy horizontally polarised photons at the output. The algorithm is described in detail in Alg.~\ref{alg:homo_LO}.} \label{fig:BS_homo}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function PhaseKeyEncoding($\vec\alpha$,$k$):
\begin{enumerate}
    \item Alice prepares the input multi-mode coherent state,
    \begin{align}
    \ket\psi_\mathrm{in} = \ket{\vec\alpha} = \ket{\alpha_1,\dots,\alpha_m}.
    \end{align}
    \item Alice chooses a random private key $k$ as a real number from the uniform distribution,
    \begin{align}
    k\in (0,2\pi).
    \end{align}
    \item Alice prepares the encoded state by applying the same phase-shift, of angle $k$, to each mode,
    \begin{align}
    \ket\psi_\mathrm{enc} = \hat\Phi(k)^{\otimes m}\ket\psi_\mathrm{in},
    \end{align}
    where,
    \begin{align}
    \hat\Phi(\phi) = e^{i\phi\hat{n}},
    \end{align}
    is the phase-shift operator.
    \item Alice sends $\ket\psi_\mathrm{enc}$ to Bob.
    \item Bob applies processing using his linear optics computer, to obtain,
    \begin{align}
    \ket\psi_\mathrm{enc\,comp} = \hat{U}\ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns $\ket\psi_\mathrm{enc\,comp}$ to Alice.
    \item Alice applies the inverse of the encoding operation,
    \begin{align}
    \ket\psi_\mathrm{comp} = \hat\Phi(-k)^{\otimes m}\ket\psi_\mathrm{enc\,comp}.
    \end{align}
    \item The resulting state is,
    \begin{align}
    \ket\psi_\mathrm{comp} = \ket{\vec\beta} = \ket{\beta_1,\dots,\beta_m},
    \end{align}
    where,
    \begin{align}
    \vec\beta = U\cdot\vec\alpha.
    \end{align}
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Protocol for implementing homomorphic encryption on coherent state passive linear optics, using phase-key encoding.} \label{alg:homo_coherent_LO}
\end{table}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{coherent_state_homo_unenc}\\
\includegraphics[width=0.475\textwidth]{coherent_state_homo_enc}
\captionspacefig \caption{Trace distance between unencoded (top) and encoded (bottom) basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. Each mode is inputted with one of two basis coherent states, \mbox{$\ket{\pm\alpha}$}. \mbox{$\mathrm{wt}(\vec{x})$} denotes the Hamming weight of bit-string $\vec{x}$. Two states are indistinguishable if their trace distance is 0, and distinguishable (orthogonal) if their trace distance is 1. Lower trace distance between encoded states implies a lower chance of Bob guessing Alice's plaintext input state.} \label{fig:homo_coh_st_tr}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=0.475\textwidth]{coherent_state_homo_unenc}
\includegraphics[width=0.475\textwidth]{coherent_state_homo_enc}
\captionspacefig \caption{Trace distance between unencoded (top) and encoded (bottom) basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. Each mode is inputted with one of two basis coherent states, \mbox{$\ket{\pm\alpha}$}. \mbox{$\mathrm{wt}(\vec{x})$} denotes the Hamming weight of bit-string $\vec{x}$. Two states are indistinguishable if their trace distance is 0, and distinguishable (orthogonal) if their trace distance is 1. Lower trace distance between encoded states implies a lower chance of Bob guessing Alice's plaintext input state.} \label{fig:homo_coh_st_tr}
\end{figure*}
\fi

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{coherent_state_homo_ratio}
\captionspacefig \caption{Ratio of the trace distance between unencoded and encoded basis states for coherent state computation using phase-key encoding, with \mbox{$d=50$} keys and \mbox{$m=10$} modes. \mbox{$R<1$} implies information hiding from Bob.} \label{fig:homo_coh_st_ratio}
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DisplacementKeyEncoding($\ket\psi$,$k$):
\begin{enumerate}
    \item Alice prepares the $m$-mode state $\ket\psi$.
    \item Alice chooses a set of independent complex displacement amplitudes as her private key,
    \begin{align}
    k=\{\alpha_1,\dots,\alpha_m\}.
    \end{align}
    \item Alice applies the displacements to each mode, yielding her encrypted state,
    \begin{align}
    \ket\psi_\mathrm{enc} = \left[\bigotimes_{i=1}^m \hat{D}_i(\alpha_i)\right] \ket\psi,
    \end{align}
    where $\hat{D}_i(\alpha_i)$ is the displacement operator for the $i$th mode, with displacement amplitude $\alpha_i$.
    \item Alice sends the encrypted state to Bob.
    \item Bob applies the computation $\hat{U}$,
    \begin{align}
    \ket\psi_\mathrm{enc\, comp} = \hat{U}\ket\psi_\mathrm{enc}.
    \end{align}
    \item Bob returns the encrypted computed state to Alice.
    \item Alice calculates the inverse displacement amplitudes $\vec\beta$,
    \begin{align}
    \vec\beta = U\cdot\vec\alpha.
    \end{align}
    \item Alice applies the inverse displacements to each mode,
    \begin{align}
    \ket\psi_\mathrm{comp} &= \left[\bigotimes_{i=1}^m \hat{D}^\dag_i(\beta_i)\right] \ket\psi_\mathrm{enc\, comp} \nonumber \\
    &= \hat{U}\ket\psi,
    \end{align}
    \item $\ket\psi_\mathrm{comp}$ is the unencrypted computed output state.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Protocol for implementing homomorphic encryption using displacement-key encoding.} \label{alg:homo_disp_LO}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{lo_displacement_homo}
\captionspacefig \caption{Circuit layout for displacement-key homomorphic encoding of passive linear optics, where \mbox{$\alpha_i'=\alpha_i/r$} and \mbox{$\beta_i'=\beta_i/r$}. Mixing the input modes with respective coherent states on a very low-reflectivity ($r$) beamsplitter implements the displacement operations. Following decoding, the output states is simply given by \mbox{$\ket{\psi_\mathrm{out}} = \hat{U}\ket{\psi_\mathrm{in}}$}, the computed input state.}\label{fig:lo_disp_key_circuit}	
\end{figure}

### 2018-09-03 Sections/essay_security_implications_of_the_global_quantum_internet.tex

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function MakeAmericaGreatAgain(Putin):
\begin{enumerate}
    \item A Russian bedroom hacker with no direct access to quantum technology, delegates a factorisation algorithm to the cloud using homomorphic encryption.
    \item The computation is physically executed on a server in the United States.
    \item The result is returned to our Russian comrade.
    \item The Russian uses the obtained private RSA key to hack Hillary's emails.
    \item The emails are strategically leaked during the next Presidential election.
    \item This swings the election in favour of Trump\texttrademark.
    \item The NSA and FBI have no clue who was behind it, since it was homomorphically encrypted.
    \item They blame Edward Snowden.
    \item Fox News\texttrademark\,calls for his execution.
    \item They'd kick themselves if they found out the algorithm was actually executed on US soil.
    \item Unless the NSA switches off the entire quantum internet, they can't prevent it from happening again in subsequent elections.
    \item return(America is Great Again\texttrademark).
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspace \caption{A typical example of a nefarious use for cloud quantum computation. See Fig.~\ref{fig:trump_tweet} for the outcome.} \label{alg:russian}\index{Trump}\index{Covfefe}
\end{table}

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{trump_tweet}
\captionspace \caption{POTUS responds to Alg.~\ref{alg:russian}.}\label{fig:trump_tweet}\index{Trump}\index{Sad}\index{Covfefe}
\end{figure}

>>>>

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function MakeAmericaGreatAgain(Putin):
\begin{enumerate}
    \item A Russian bedroom hacker with no direct access to quantum technology, delegates a factorisation algorithm to the cloud using homomorphic encryption.
    \item The computation is physically executed on a server in the United States.
    \item The result is returned to our Russian comrade.
    \item The Russian uses the obtained private RSA key to hack Hillary's emails.
    \item The emails are strategically leaked during the next Presidential election.
    \item This swings the election in favour of Trump\texttrademark.
    \item The NSA and FBI have no clue who was behind it, since it was homomorphically encrypted.
    \item They blame Edward Snowden.
    \item Fox News\texttrademark\,calls for his execution.
    \item They'd kick themselves if they found out the algorithm was actually executed on US soil.
    \item Unless the NSA switches off the entire quantum internet, they can't prevent it from happening again in subsequent elections.
    \item return(America is Great Again\texttrademark).
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{A typical example of a nefarious use for cloud quantum computation. See Fig.~\ref{fig:trump_tweet} for the outcome.} \label{alg:russian}\index{Trump}\index{Covfefe}
\end{table}

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{trump_tweet}
\captionspacefig \caption{POTUS responds to Alg.~\ref{alg:russian}.}\label{fig:trump_tweet}\index{Trump}\index{Sad}\index{Covfefe}
\end{figure}

### 2018-09-03 Sections/essay_the_economics_of_the_quantum_internet.tex

Already today, even before the advent of useful post-classical quantum computers, we are seeing the emergence of the outsourced model for computation\index{Outsourced quantum computation}. IBM recently made an elementary 16-qubit quantum computer freely available for use via the cloud. Interested users can log in online, upload a circuit description for a quantum protocol, and have it executed remotely, with the results relayed back in real-time. Although still very primitive, this simple development already makes experimentation with elementary quantum protocols accessible to the poor layman, undergrad, or PhD student in a developing country, people who just last year would never have dreamt of being able to run their own quantum information processing experiments! This effectively opens up research opportunities to people who otherwise would have been priced out of the market entirely, unable to compete with established, well-resourced labs. Evidently, the market already recognises the importance of outsourced models for quantum computation. We encourage the impatiently curious reader to log onto the `IBM Quantum Experience' (\texttt{\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}}) and take a shot at designing a 16-qubit quantum protocol, without even needing to be in the same country as the quantum computer.

>>>>

Already today, even before the advent of useful post-classical quantum computers, we are seeing the emergence of the outsourced model for computation\index{Outsourced quantum computation}. IBM recently made an elementary 16-qubit quantum computer freely available for use via the cloud. Interested users can log in online, upload a circuit description for a quantum protocol, and have it executed remotely, with the results relayed back in real-time. Although still very primitive, this simple development already makes experimentation with elementary quantum protocols accessible to the poor layman, undergrad, or PhD student in a developing country, people who just last year would never have dreamt of being able to run their own quantum information processing experiments! This effectively opens up research opportunities to people who otherwise would have been priced out of the market entirely, unable to compete with established, well-resourced labs. Evidently, the market already recognises the importance of outsourced models for quantum computation. We encourage the impatiently curious reader to log onto the `IBM Quantum Experience' (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}) and take a shot at designing a 16-qubit quantum protocol, without even needing to be in the same country as the quantum computer.
